---
title: "SpASM"
output: html_notebook
---

This repo is an updated version of the GASP module developed for Ovando et al. 2016 Fish and Fisheries. 

Development is centered around support of 


# Next ideas


```{r}
library(tidyverse)
library(spasm)
library(stringr)
library(rfishbase)
library(modelr)
library(Rcpp)
library(RcppEigen)

# sourceCpp("scripts/eigen_mat_mult.cpp")

fish <- create_fish(adult_movement = 1e-3,
                    larval_movement = 1e-3,
                    density_dependence_form = 1,
                    price = 10,
                    query_fishbase = F,
                    linf = 100,
                    age_mature = 2,
                    vbk = .2,
                    t0 = 0,
                    max_age = 20,
                    weight_a = 1e-3,
                    weight_b = 3)

fleet <-
  create_fleet(
    eq_f = .2,
    length_50_sel = 50,
    length_95_sel = 52,
    fish = fish,
    mpa_reaction = 'concentrate',
    price = 1,
    cost = 1000,
    beta = 1.3,
    theta = 1e-1,
    q = 1e-3,
    fleet_model = 'open-access',
    effort_allocation = 'gravity',
    initial_effort = 10,
    target_catch = 1
  )

tester <-
  spasm::sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 35
  )

tester %>%
  group_by(year) %>%
  summarise(effort = sum(effort),
            profits = sum(profits),
            f = max(f),
            catch = sum(biomass_caught),
            total_ssb = sum(ssb)) %>%
  ggplot(aes(year, total_ssb)) +
  geom_point()


```


1. Make a "profit-gravity" model, where they distribute themselves by profits in each patch, allowing for heterogeneous costs in each patch


```{r}
fleet$effort_allocation <- 'profit-gravity'
fleet$fleet_model <- 'constant-effort'
tester <-
  spasm::sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 35
  )

tester %>% 
  group_by(year, patch) %>% 
  summarise(te = sum(effort, na.rm = T))

```

OK that works now. Now, add in ability to have cost vary by patch. 

```{r}
fleet$cost_slope <-  0.1

fleet$cost_function <- 'distance from port'


tester <-
  spasm::sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 35
  )


tester %>% 
  group_by(year, patch) %>% 
  summarise(te = sum(effort, na.rm = T))


```



2. Allow q to vary by time

3. Allow habitat to vary

4. Incorporate sampling of length structure into model 

5. Add in recruitment variability and autocorrelation

This is a scotch project at home


