---
title: "SpASM"
output: html_notebook
---

This repo is an updated version of the GASP module developed for Ovando et al. 2016 Fish and Fisheries. 

Development is centered around support of 


# Next ideas


```{r}

# demons::load_functions('../R')
# load("../data/lhi.rda")
library(tidyverse)
library(spasm)
library(stringr)
library(rfishbase)
library(modelr)
library(Rcpp)
library(RcppEigen)
library(viridis)
library(LIME)
library(LBSPR)

# sourceCpp("scripts/eigen_mat_mult.cpp")

fish <- create_fish(adult_movement = 1e-3,
                    larval_movement = 1e-3,
                    density_dependence_form = 1,
                    price = 10,
                    query_fishbase = F,
                    linf = 100,
                    age_mature = 2,
                    vbk = .2,
                    t0 = 0,
                    min_age = 0,
                    max_age = 20,
                    time_step = 1,
                    weight_a = 1e-3,
                    weight_b = 3)


fleet <-
  create_fleet(
      eq_f = .2,
    length_50_sel = 50,
    delta = 2,
    fish = fish,
    mpa_reaction = 'concentrate',
    price = 1,
    cost = 1000,
    beta = 1.3,
    theta = 1e-1,
    q = 1e-3,
    fleet_model = 'open-access',
    effort_allocation = 'gravity',
    initial_effort = 10,
    target_catch = 1
  )

```


1. Make a "profit-gravity" model, where they distribute themselves by profits in each patch, allowing for heterogeneous costs in each patch


```{r}
fleet$effort_allocation <- 'profit-gravity'
fleet$fleet_model <- 'constant-effort'

tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 1,
    burn_year = 25,
    sim_years = 50
  )

tester %>% 
  group_by(year, patch) %>% 
  summarise(te = sum(effort, na.rm = T))

```

OK that works now. Now, add in ability to have cost vary by patch. 

```{r}
fleet$cost_slope <-  0.1

fleet$cost_function <- 'distance from port'


tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 10
  )


tester %>% 
  group_by(year, patch) %>% 
  summarise(te = sum(effort, na.rm = T))


```

2. Allow q to vary by time


```{r}
fleet$tech_rate <- 0.1

tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 10
  )

tester %>% 
  group_by(year) %>% 
  summarise(tf = sum(f, na.rm = T))



```


4. Add in recruitment variability and autocorrelation



```{r}

fish$t0 <- -0.1

fish$sigma_r <- 0

fish$rec_ac <- 0

fleet$tech_rate <- 0.1

fleet$initial_effort <-  1000

tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 2,
    burn_year = 25,
    sim_years = 10
  )

tester %>% 
  filter(age == 1) %>% 
  group_by(year) %>% 
  summarise(tn = sum(numbers, na.rm = T)) %>% 
  ggplot(aes(year, tn)) + 
  geom_point()

```

5. Incorporate sampling of length structure into model 

No need to do this in the model, you can sample from the numbers at age afterwords. 

```{r}

n_at_age <- tester %>% 
  filter(year == max(year)) %>% 
  select(patch,age, numbers, numbers_caught)

length_samples <- sample_lengths(n_at_age = n_at_age,
                                 cv = 0.1,
                                 k = fish$vbk,
                                 linf = fish$linf,
                                 t0 = fish$t0,
                                 sample_type = 'catch',
                                 percent_sampled = 1,
                                 time_step = 1)

    length_samples %>%
      ggplot(aes(length_bin, numbers)) +
      geom_col()

```


And now, age those length samples. 


```{r}

age_samples <- length_to_age(length_samples = length_samples,
                             cv = 0.1,
                             k = fish$vbk,
                             linf = fish$linf,
                             t0 = fish$t0,
                             max_age = fish$max_age,
                             min_age = fish$min_age,
                             time_step = fish$time_step)

age_samples$numbers %>% sum()

wtf <- tester %>% filter(year == max(year)) %>% select(age,patch,numbers_caught) %>%
  group_by(age) %>% summarise(numbers = sum(numbers_caught)) %>% 
mutate(age_type = 'true') 

sum(wtf$numbers)

age_samples %>% 
  mutate(age_type = 'sampled') %>% 
  bind_rows(wtf) %>% 
  ggplot(aes(age,numbers, fill = age_type)) + 
  geom_col(position = 'dodge')


tester %>% 
  ggplot(aes(age,1 - exp(-f))) + 
  geom_col(aes(fill = factor(patch)), position = 'dodge') + 
  facet_wrap(~year)
  

tester %>% 
  select(year,age,numbers, numbers_caught, patch) %>% 
  gather('number_type','number',numbers:numbers_caught) %>% 
  group_by(year, age,number_type) %>% 
  summarise(tn = sum(number, na.rm = T)) %>% 
  ggplot(aes(age,tn, fill = number_type)) + 
  geom_col(position = 'dodge') + 
  facet_wrap(~year)

tester %>% 
  group_by(year,age) %>% 
  summarise(numbers = sum(numbers)) %>% 
  ggplot(aes(age,numbers)) + 
  geom_col() + 
  facet_wrap(~year)
  

tester %>% 
  group_by(year,patch) %>% 
  summarise(te = sum(effort)) %>% 
  ggplot(aes(patch, te, color = factor(year))) + 
  geom_line()


```

Bring it all on home


```{r}

fleet$cost_slope <-  0.1

fleet$cost_function <- 'distance from port'

fish$t0 <- -0.1

fish$sigma_r <- 0.75

fish$rec_ac <- 0

fleet$tech_rate <- 0.1

fleet$initial_effort <-  1000

fleet$effort_allocation <- 'profit-gravity'

fleet$fleet_model <- 'constant-effort'

fleet$price <-  100

fleet$cost <- 10

fleet$theta = 2e-3


tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 10,
    burn_year = 25,
    sim_years = 10
  )

tester %>% 
  group_by(year) %>% 
  summarise(
    tb = sum(ssb),
    te = sum(effort),
            tp = sum(profits)) %>% 
              ggplot(aes(tb, te)) + 
              geom_path()

```


```{r}
tester %>% 
  group_by(year, age) %>% 
  summarise(tn = sum(numbers)) %>% 
  ggplot(aes(age, tn, color = year)) + 
  geom_line(position = 'dodge', alpha = 0.5, size = 1.5) + 
  facet_grid(year ~ . , as.table = F) + 
  theme_classic() + 
  theme(axis.text.y = element_blank(),
        panel.spacing = unit(0,'cm'),
        strip.background = element_blank(),
        strip.text = element_blank()) + 
  scale_color_viridis()

```


```{r}
tester %>% 
  group_by(year,patch) %>% 
  summarise(te = sum(effort)) %>% 
  ggplot(aes(patch, te, color = factor(year))) + 
  geom_line()
```

check length sampling
```{r}

n_at_age <- tester %>% 
  filter(year == max(year)) %>% 
  select(patch,age, numbers, numbers_caught)

length_samples <- sample_lengths(n_at_age = n_at_age,
                                 cv = 0.1,
                                 k = fish$vbk,
                                 linf = fish$linf,
                                 t0 = fish$t0,
                                 sample_type = 'catch',
                                 percent_sampled = 1,
                                 time_step = fish$time_step)

    length_samples %>%
      ggplot(aes(length_bin, numbers)) +
      geom_col()

```


```{r}

length_samples <- tester %>% 
  select(year,patch,age, numbers, numbers_caught) %>% 
  nest(-year) %>% 
  mutate(length_samples = map(data, ~sample_lengths(n_at_age = .x,
                                                   cv = 0.1,
                                                    k = fish$vbk,
                                 linf = fish$linf,
                                 t0 = fish$t0,
                                 sample_type = 'catch',
                                 percent_sampled = 1,
                                 fish$time_step))) %>% 
  select(-data) %>% 
  unnest()


length_samples %>% 
  ggplot(aes(length_bin, numbers, color = year)) + 
  geom_line(position = 'dodge', alpha = 0.5, size = 1.5) + 
  facet_grid(year ~ . , as.table = F) + 
  theme_classic() + 
  theme(axis.text.y = element_blank(),
        panel.spacing = unit(0,'cm'),
        strip.background = element_blank(),
        strip.text = element_blank()) + 
  scale_color_viridis()

```

check age sampling
```{r}

    age_samples <- length_to_age(length_samples = length_samples,
                             cv = 0.1,
                             k = fish$vbk,
                             linf = fish$linf,
                             t0 = fish$t0,
                             max_age = fish$max_age,
                             min_age = fish$min_age,
                             time_step = fish$time_step)

age_samples %>% 
  mutate(age_type = 'sampled') %>% 
  bind_rows(wtf) %>% 
  ggplot(aes(age,numbers, fill = age_type)) + 
  geom_col(position = 'dodge')


tester %>% 
  ggplot(aes(age,1 - exp(-f))) + 
  geom_col(aes(fill = factor(patch)), position = 'dodge') + 
  facet_wrap(~year)
  

tester %>% 
  select(year,age,numbers, numbers_caught, patch) %>% 
  gather('number_type','number',numbers:numbers_caught) %>% 
  group_by(year, age,number_type) %>% 
  summarise(tn = sum(number, na.rm = T)) %>% 
  ggplot(aes(age,tn, fill = number_type)) + 
  geom_col(position = 'dodge') + 
  facet_wrap(~year)

tester %>% 
  group_by(year,age) %>% 
  summarise(numbers = sum(numbers)) %>% 
  ggplot(aes(age,numbers)) + 
  geom_col() + 
  facet_wrap(~year)
  
```

This is a scotch project at home

# What the hell is going on

I can't convince myself that the hockey stick in mortality isn't a big somehow. So, how to debug this. 

1. Create an artificial spike in the F rates and see if it propogates perfectly through the age structure 

2. Write out a simple little loop population and test it that way

3. Track the mortality it each cohort in the model itself and predict it. 

4. Check for a normal bug again. 


```{r}

fish <- create_fish(adult_movement = 1e-3,
                    larval_movement = 1e-3,
                    density_dependence_form = 1,
                    price = 10,
                    query_fishbase = F,
                    linf = 65,
                    vbk = .2,
                    t0 = -0.01,
                    cv_len = 0.2,
                    length_mature =  34,
                    m = 0.2,
                    min_age = 0,
                    max_age = floor(-log(0.01) / 0.2),
                    time_step = 1,
                    weight_a = 0.0245,
                    weight_b = 2.79, 
                    sigma_r = 0,
                    rec_ac = 0)

fleet <-
  create_fleet(
    length_50_sel = 0.25*fish$linf,
    delta = 1,
    fish = fish,
    mpa_reaction = 'concentrate',
    price = 1,
    cost = 1000,
    beta = 1.3,
    theta = 1e-1,
    q = 1e-3,
    fleet_model = 'constant-effort',
    effort_allocation = 'simple',
    initial_effort = 0,
    target_catch = 0
  )


fish$rec_ac <- 0

fish$sigma_r <- 0

fish$cv_len <- 0

fish$m <- 0.1

fish$max_age <- 100

fish <- update_fish(fish)

fleet$length_50_sel <- 0* fish$linf

fleet$initial_effort <- 200

fleet <- update_fleet(fleet, fish)

  cc_fishery <- sim_fishery(fish = fish, fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 1,
    burn_year = 30,
    sim_years = 70
  )

  
  
test_data <- cc_fishery %>% 
  ungroup() %>% 
  filter(year == max(year)) %>% 
  group_by(age) %>% 
  summarise(numbers = sum(numbers)) %>% 
  mutate(log_numbers = log(numbers)) %>% 
  ungroup()

peak_age <- test_data$age[test_data$numbers == max(test_data$numbers)]

cc <- lm(log_numbers ~ age, data = test_data)

summary(cc)

cc_fishery$f %>% unique() + fish$m

test_data %>% 
  ggplot(aes(age, log_numbers)) + 
  geom_point()

```

```{r}


n_mat <- matrix(NA, nrow = 20, ncol = 20)

n_mat[,1] <-  100

n_mat[1,] <-  100 * exp(-.1 * 0:19)

 fs <-  c(rep(.1,10), rep(.8,10))
 
 fs <- rlnorm(20, log(.2),2)

for (t in 2:20){
  
  n_mat[t,2:20] <- n_mat[t - 1,1:19] * exp(-fs[t])
  
  }
  
wtf <- n_mat[20,] %>% log()

data_frame(a = wtf, b = lead(wtf,1)) %>% 
  mutate(survival = b - a,
         fs = rev((-fs)))

plot(wtf)



```

Well I'll be damned. The mortality rate 10 years ago is burned in the the survival of age 25 year old individuals (the slope from 25 to 26). Which I guess makes some sense. 25 years ago X% survived to age 26. 

And duh, it doesn't work perfectly once you throw in a recruitment function since it's no longer a constant input, at least until it hits equilibirum. So, you're putting in less fish, which makes the survival rate actually a bit higher than you'd think, since there are proportionally more older fish than under constant recruitment

# Test assessment modules

A catch curve

```{r}


fish <- create_fish(adult_movement = 1e-3,
                    larval_movement = 1e-3,
                    density_dependence_form = 1,
                    price = 10,
                    query_fishbase = F,
                    linf = 65,
                    vbk = .2,
                    t0 = -0.01,
                    cv_len = 0,
                    length_50_mature  =  37,
                    length_95_mature = 38,
                    m = 0.2,
                    min_age = 0,
                    max_age = floor(-log(0.01) / fish$m),
                    time_step = 0.25,
                    weight_a = 0.0245,
                    weight_b = 2.79, 
                    sigma_r = 0,
                    rec_ac = 0)

fleet <-
  create_fleet(
    length_50_sel = 0.25*fish$linf,
    delta = 1,
    fish = fish,
    mpa_reaction = 'concentrate',
    price = 1,
    cost = 1000,
    beta = 1.3,
    theta = 1e-1,
    q = 1e-3,
    fleet_model = 'constant-effort',
    effort_allocation = 'simple',
    initial_effort = 0,
    target_catch = 0
  )


fish$rec_ac <- 0

fish$sigma_r <- 0

fish$cv_len <- 0

fish$max_age <- ((-log(0.01)/fish$m)/fish$time_step) %>% floor()

fish <- update_fish(fish)

fleet$length_50_sel <- 0* fish$linf

fleet$initial_effort <- 50

fleet <- update_fleet(fleet, fish)

  cc_fishery <- sim_fishery(fish = fish, fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 1,
    burn_year = 100,
    sim_years = 300
  )


n_at_age <- cc_fishery %>% 
  filter(year == max(year)) %>% 
  select(patch,age, numbers, numbers_caught)

length_samples <- sample_lengths(n_at_age = n_at_age,
                                 cv = fish$cv_len,
                                 k = fish$vbk,
                                 linf = fish$linf,
                                 t0 = fish$t0,
                                 sample_type = 'population',
                                 percent_sampled = 1,
                                 time_step = fish$time_step) %>% 
  mutate(year = 1)

z <- run_catch_curve(length_comps = length_samples, fish = fish)
z
mean(cc_fishery$f) + fish$m

```

OK so it's not that, the length resampling works 

LBSPR

```{r}


lbspr_fish <-  new("LB_pars")

lbspr_fish@Species <- 'WTF'

lbspr_fish@Linf <- fish$linf

lbspr_fish@M <- fish$m

lbspr_fish@MK <- fish$m / fish$vbk

lbspr_fish@Steepness <- fish$steepness

# lbspr_fish@CVLinf <- fish$cv_len

lbspr_fish@L50 <- fish$length_50_mature

lbspr_fish@L95 <- fish$length_95_mature

lbspr_fish@Walpha <- fish$weight_a
# 
lbspr_fish@Wbeta <- fish$weight_b

lbspr_fish@SL50 <- fleet$length_50_sel

lbspr_fish@SL95 <- fleet$length_50_sel + fleet$delta

lbspr_fish@FM <- f_v_m

lbspr_fish@BinWidth <- 1

lbspr_fish@L_units <- 'cm'

lbspr_sim <- LBSPRsim(lbspr_fish, Control = list(modtype = 'absel', Nage = fish$max_age))

plotSim(lbspr_sim)
 
lbspr_lengths <- new("LB_lengths", LB_pars=lbspr_fish, dataType = 'freq')

lbspr_lens <- length_samples %>%
  spread(year,numbers) %>% 
  mutate(length_bin = length_bin + 0.5) %>% 
  rename(LMids = length_bin) %>% 
  as.matrix()

  lbspr_lengths@LData <- lbspr_lens[,-1] %>% as.matrix()
  
  lbspr_lengths@LMids <- lbspr_lens[,1] %>% as.numeric()
  
  lbspr_lengths@NYears <- ncol(lbspr_lens) - 1 # - 1
  
  lbspr_lengths@Years <- 1:lbspr_lengths@NYears 
    
  lbspr_fit <- LBSPRfit(lbspr_fish, lbspr_lengths,Control = list(modtype = 'absel', Nage = fish$max_age + 2))

  a = fit_lbspr(fish = fish, fleet = fleet, length_comps = length_samples)


```
```{r}
plotSize(lbspr_fit)

lbspr_fit@SL95

lbspr_fit@FM

```

So close!!!

Let's do one more check and see if you get the same unfished population





Check LIME against LBSPR
```{r}


 vbk = 0.21
    linf = 64.58
    lwa = 0.0245
    lwb = 2.79
    S50 = 30
    selex_input = "length"
    M50 = 34
    maturity_input = "length"
    binwidth = 1
    CVlen = 0.1
    SigmaR = 0
    M = 0.2
    rho = 0
  
  
  lh <-
  create_lh_list(
    vbk = vbk,
    linf = linf,
    lwa = lwa,
    lwb = lwb,
    S50 = S50,
    selex_input = selex_input,
    M50 = M50,
    maturity_input = maturity_input,
    binwidth = binwidth,
    CVlen = CVlen,
    SigmaR = SigmaR,
    M = M,
    rho = rho,
    F1 = 0.2,
    SigmaF = 0
  )
  
  simmed_fish <- sim_pop(
  lh = lh,
  Nyears = 50,
  Fdynamics = 'Constant',
  Rdynamics = 'BH',
  nburn = 5,
  modname = 'blah',
  seed = 42,
  init_depl = 0,
  comp_sample = 1000,
  pool = T,
  Nyears_comp = 50,
  mismatch = F
)
  
  plot(1:length(simmed_fish$LF),simmed_fish$LF)
  

  lbspr_lengths <- simmed_fish$LF %>%
  t() %>% 
  as_data_frame() %>% 
  set_names(1:dim(.)[2])

lbspr_lengths <- data.frame(LMids = simmed_fish$mids %>% as.numeric(),lbspr_lengths, check.names = F)


babel_lengths <- new("LB_lengths")

babel_lengths@LMids <- simmed_fish$mids

babel_lengths@LData <- lbspr_lengths %>% as.matrix()
  
  babel_lengths@Years <-
  as.numeric(lbspr_lengths %>% select(-LMids) %>% colnames())

babel_lengths@NYears <- length(babel_lengths@Years)

babel_pars <- new("LB_pars")

babel_pars@Species <- "babelfish"

babel_pars@Linf <- linf

babel_pars@L50 <- M50

babel_pars@L95 <-  M50+1

babel_pars@MK <- M / vbk

babel_pars@BinWidth <- 1

babel_fit <- LBSPRfit(babel_pars, babel_lengths,
                      yrs = 1:babel_lengths@NYears)


real <- data_frame(year = 1:50, spr = simmed_fish$SPR_t, name = 'True Value')

lbspr <- data_frame(year = 1:50, spr = babel_fit@SPR, name = 'LBSPR Estimate')

```


# Checking on selectivity

It seems like something is going wrong in the length sampling; the length comps don't seem to be matching selecitivity. 


```{r}

fleet$length_50_sel

check <- sim_sampling(fish = fish, fleet = fleet)

check <- check %>% 
  filter(year == max(year))

check %>% 
select(n_at_age) %>% 
  unnest() %>% 
  mutate(sel = fleet$sel_at_age,
         mean_length = fish$length_at_age) %>% 
  ggplot(aes(age,numbers_caught, fill = sel)) + 
  geom_point(shape = 21)

```

So that looks good, so I'm guessing that there's a problem in the conversion from age to length in the length sampling. 

```{r}

check %>% 
select(catch_ages_samples) %>% 
  unnest() %>% 
  mutate(sel = fleet$sel_at_age,
         mean_length = fish$length_at_age) %>% 
  ggplot(aes(age,numbers, fill = sel)) + 
  geom_point(shape = 21)

```

```{r}

check %>% 
select(catch_length_samples) %>% 
  unnest() %>% 
  ggplot(aes(length_bin,numbers)) + 
  geom_point(shape = 21) + 
  geom_vline(aes(xintercept = fleet$length_50_sel))

```


```{r}

lbspr_sim <- LBSPRsim(lbspr_fish, Control = list(modtype = 'absel', Nage = fish$max_age + 2))


spasm_lengths <- check %>% 
  filter(year == max(year)) %>% 
  select(pop_length) %>% 
  unnest() %>% 
  mutate(source = 'spasm')

lbspr_lengths <- lbspr_sim@pLPop %>% 
  as_data_frame() %>% 
  select(LMids, PopUF) %>% 
  rename(length_bin = LMids,numbers = PopUF) %>% 
  mutate(source = 'lbspr')

comp_lengths <- spasm_lengths %>% 
  bind_rows(lbspr_lengths) %>% 
  group_by(source) %>% 
  mutate(pnumbers = numbers / sum(numbers)) 

comp_lengths %>% 
  ggplot(aes(length_bin, pnumbers, fill = source)) + 
  geom_point(shape = 21) + 
  geom_vline(data = data_frame(lata = fish$length_at_age %>% floor()), aes(xintercept =lata))

```

AHA. Setting Nage to max_age + 2 seems to do the trick, probably to account for the fact that you don't have a zero, plus some other goofiness. 

So the last question, why the hell aren't the distributions perfectly centered on the mean length_at_age values?, ah not a problem, just an artifact of Geom_col

# Move to flexible time

```{r}
fish <- create_fish(adult_movement = 1e-3,
                    larval_movement = 1e-3,
                    density_dependence_form = 1,
                    price = 10,
                    query_fishbase = F,
                    linf = 100,
                    age_mature = 2,
                    vbk = .2,
                    t0 = -0.01,
                    min_age = 0,
                    max_age = 20,
                    time_step = 1,
                    weight_a = 1e-3,
                    weight_b = 3)


fleet <-
  create_fleet(
      eq_f = .2,
    length_50_sel = 50,
    delta = 2,
    fish = fish,
    mpa_reaction = 'concentrate',
    price = 1,
    cost = 1000,
    beta = 1.3,
    theta = 1e-1,
    q = 1e-3,
    fleet_model = 'open-access',
    effort_allocation = 'gravity',
    initial_effort = 10,
    target_catch = 1
  )

fleet$effort_allocation <- 'profit-gravity'
fleet$fleet_model <- 'constant-effort'

tester <-
  sim_fishery(
    fish = fish,
    fleet = fleet,
    manager  = create_manager(mpa_size = 0, year_mpa = 10),
    num_patches = 1,
    burn_year = 25,
    sim_years = 50
  )

```

